Homeless Shelter Usage Trends and Mortality: A Correlation Analysis

### 2024-04-15 paper/paper.qmd
added to model script + model rds file

library(tidyverse)
library(palmerpenguins)
```

>>>>

library(tidyverse)
library(palmerpenguins)

# THIS IS TEMPORARILY HERE -- POISSON MODEL GRAPH
predicted_counts <- predict(poisson_model, type = "response")

# Create a scatter plot of observed vs. predicted counts
plot(cleaned_data$Returned.to.shelter, cleaned_data$Deaths, 
     xlab = "Returned to shelter", ylab = "Deaths",
     main = "Observed vs. Predicted Counts",
     pch = 16, col = "blue")
lines(cleaned_data$Returned.to.shelter, predicted_counts, col = "red", type = "l", lwd = 2)
legend("topright", legend = c("Observed", "Predicted"), 
       col = c("blue", "red"), pch = c(16, NA), lty = c(NA, 1), lwd = c(NA, 2))

```
